DRAFT \\ From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics

### 2016-11-11 2015CompleteDerivation/completeDerivation.tex
Minor improvements on prelude for quantum

Before introducing assumption \ref{ass:irreducibility} and deriving quantum mechanics as its consequence, we first give a semi-classical account of the conceptual model we will be using. This allows to build the intuition more gradually and to show that classical and quantum mechanics are not as different as one may first imagine.

We will see that, as a first approximation, quantum particles are more keenly described by classical composite states (i.e. a distribution in phase space) like any other object made of a finite amount of material. We'll also see that classical distributions already possess qualitative properties that are typically associated with quantum systems, including a classical analogue of the uncertainty principle.

@@

We now ask the following question: once we fix the entropy, what is the relationship between the spread of the marginal distributions along $q$ and $p$? Using Lagrange multipliers, we fix the total amount of material to $1$ and the total entropy $I_0$ and find the distribution that minimizes the the product of the variance $\sigma_q^2 \sigma_p^2 = \int (q-\mu_q)^2 \rho \, dqdp \int (p-\mu_p)^2 \rho \, dqdp$.
\begin{align*}
L = &\int (q-\mu_q)^2 \rho \, dqdp \int (p-\mu_p)^2 \rho \, dqdp \\
&+ \lambda_1(\int \rho dqdp - 1)\\
&+ \lambda_2(- \int \rho \ln \rho \, dqdp - I_0)\\
\delta L = &\int \delta \rho [(q-\mu_q)^2 \sigma_p^2 + \sigma_q^2 (p-\mu_p)^2 \\ &+ \lambda_1 - \lambda_2 \ln \rho - \lambda_2 ] dqdp = 0 \\
\lambda_2 \ln \rho = &\lambda_1 - \lambda_2 + (q-\mu_q)^2 \sigma_p^2 + \sigma_q^2 (p-\mu_p)^2 \\
\rho = &e^{\frac{\lambda_1 - \lambda_2}{\lambda_2}}e^{\frac{(q-\mu_q)^2 \sigma_p^2}{\lambda_2}}e^{\frac{\sigma_q^2 (p-\mu_p)^2}{\lambda_2}}\\
\rho = &\frac{1}{ 2 \pi \sigma_q \sigma_p} e^{-\frac{(q-\mu_q)^2}{2\sigma_q^2}} e^{-\frac{(p-\mu_p)^2}{2\sigma_p^2}} \\
I_0 = &\ln (2\sigma_q\sigma_p\pi) + 1
\end{align*}
(TODO: move the details of the math) We find that the distribution that minimizes the spread is the product of two independent Gaussians. Recall that in quantum mechanics, the Gaussian wave packet is the state that minimizes uncertainty: this is the classical analogue.

>>>>

Before introducing assumption \ref{ass:irreducibility} and deriving quantum mechanics as its consequence, we first give a semi-classical account of the conceptual model we will be using. This allows us to build the intuition more gradually and to show that classical and quantum mechanics are not as different as one may first imagine.

We will see that, as a first approximation, quantum particles are more keenly described by classical composite states (i.e. distributions in phase space) like any other object made of a finite amount of material. We'll also see that classical distributions already possess qualitative properties that are typically associated with quantum systems, including a classical analogue of the uncertainty principle.

@@

We now ask the following question: once we fix the entropy, what is the relationship between the spread of the marginal distributions along $q$ and $p$? Using Lagrange multipliers, we fix the total amount of material to $1$ and the total entropy $I_0$ and find the distribution that minimizes the the product of the variance $\sigma_q^2 \sigma_p^2 = \int (q-\mu_q)^2 \rho \, dqdp \int (p-\mu_p)^2 \rho \, dqdp$.
\begin{align*}
L = &\int (q-\mu_q)^2 \rho \, dqdp \int (p-\mu_p)^2 \rho \, dqdp \\
&+ \lambda_1(\int \rho dqdp - 1)\\
&+ \lambda_2(- \int \rho \ln \rho \, dqdp - I_0)\\
\delta L = &\int \delta \rho [(q-\mu_q)^2 \sigma_p^2 + \sigma_q^2 (p-\mu_p)^2 \\ &+ \lambda_1 - \lambda_2 \ln \rho - \lambda_2 ] dqdp = 0 \\
\lambda_2 \ln \rho = &\lambda_1 - \lambda_2 + (q-\mu_q)^2 \sigma_p^2 + \sigma_q^2 (p-\mu_p)^2 \\
\rho = &e^{\frac{\lambda_1 - \lambda_2}{\lambda_2}}e^{\frac{(q-\mu_q)^2 \sigma_p^2}{\lambda_2}}e^{\frac{\sigma_q^2 (p-\mu_p)^2}{\lambda_2}}\\
\end{align*}
We solve the multipliers and have:
\begin{align*}
\rho = &\frac{1}{ 2 \pi \sigma_q \sigma_p} e^{-\frac{(q-\mu_q)^2}{2\sigma_q^2}} e^{-\frac{(p-\mu_p)^2}{2\sigma_p^2}} \\
I_0 = &\ln (2\sigma_q\sigma_p\pi) + 1
\end{align*}
We find that the distribution that minimizes the spread is the product of two independent Gaussians. Recall that in quantum mechanics, the Gaussian wave packet is the state that minimizes uncertainty: this is the classical analogue.
